\documentclass{article}

\usepackage[paper=letterpaper,margin=1in]{geometry}
\usepackage{libertine}

\title{WCP--52: Weekly Status Report}
\date{Week of Oct. 10, 2014}
\author{WCP--52}

\begin{document}

\noindent \textbf{WCP52:} Weekly Status Report \\
Week of Oct. 10, 2014.

\subsection*{Chris Pavlina}
\begin{enumerate}
\item{Hours spent:
    \begin{enumerate}
    \item{Meeting: 1}
    \item{EDA software preparation: 3}
    \end{enumerate}
}
\item{Accomplishments
    \begin{enumerate}
    \item{Finalized first draft of specifications}
    \item{Supplied KiCad build to team}
    \end{enumerate}
}
\item{Problems and Suggestions
    \begin{enumerate}
    \item{A few of the PRS items need to be corrected still}
    \end{enumerate}
}
\item{Plans
    \begin{enumerate}
    \item{Finish brainstorming ``premortem analysis''}
    \item{Begin designing test procedures}
    \end{enumerate}
}
\end{enumerate}

\subsection*{Harrison Owens}
\begin{enumerate}
\item{Accomplishments
    \begin{enumerate}
    \item{Discussed  Project requirement specification draft with Faculty Advisor and made Appropriate changes}
    \item{Started brainstorming  our ``Pre Mortem'' test or events that could go wrong while building the project
        \begin{enumerate}
        \item{Problems in software testing}
        \item{Problems in Supply chain}
        \item{Problems with budget}
        \end{enumerate}
    }
    \end{enumerate}
}
\item{Problems
    \begin{enumerate}
    \item{Found that we need to be more specific about our requirements as they will be graded}
    \item{There were a couple of important requirements that were missing such as the safety protocols}
    \end{enumerate}
}
\item{Plans
    \begin{enumerate}
    \item{As a group continue to practice making circuits using KiCad}
    \item{Research methods on how to implement each part of the block diagram}
    \end{enumerate}
}
\end{enumerate}

\subsection*{Ken Zach}

\begin{enumerate}
\item{Hours spant working on project:
    \begin{enumerate}
    \item{Meeting: 1.5 hours}
    \item{KiCad: 1.5 hours}
    \end{enumerate}
}
\item{Problems/Solutions
\begin{enumerate}
\item{None}
\end{enumerate}
}
\item{Plans
\begin{enumerate}
\item{start considering overall system architecture}
\item{do some research on how things can be accomplished (especially calculating phase)}
\item{look over project requirements before the final submission}
\end{enumerate}
}
\end{enumerate}

\subsection*{Kaidi Xu}

We team members had a meeting this Monday at senior design lab. During this
meeting, we improved our Project Requirements Specification. We added some
requirements and struck several requirements from the suggestions that Kyle
give us last week. And our leader also made the KiCad let us to download.

We have a meet today with Professor Kyle, and show him our Project Requirements
Specification. And here are something needs us to notice and change. 

\begin{enumerate}
\item{We need to change something about the standard Bode Plot spec.
    \begin{enumerate}
    \item{describe what is meant by standard bode plot or get rid of the word standard.}
    \item{or a plot of gain with respect to frequency.}
    \end{enumerate}
}
\item{SHALL go to 150MHz, and SHOULD go to 200MHz and keep amplitude spec up to 100 MHz}
\item{3.2.5 change 80 to 60, and SHALL do 30dB instead of 40dB and should do 60dB.}
\item{should have a more precise phase accuracy(3 degrees)}
\end{enumerate}

Here is something we need to think about that might kill our project at the
last, and know how we will avoid these problems.
\begin{itemize}
\item{supply chain issues}
\item{budget issues }
\item{run out of time for software/testing }
\item{general test-ability issues}
\item{prototype breaking}
\end{itemize}

From next week our next step is to figure out overall system architecture. We
need to go high level than the system block diagram on the project write up. It
needs to contain functional blocks and do not forget about power distribution.-
figure out what is the best way to calculate phase.-figure out what might be
the most difficult pieces and begin designing in such a way that make those
difficult pieces easiest.


\end{document}

