\begin{thebibliography}{9}

\bibitem{aod417}
Alpha \& Omega Semiconductor, ``AOD417 P-Channel Enhancement Mode Field Effect Transistor,''
AOD417 datasheet, 2008. \url{http://aosmd.com/pdfs/datasheet/AOD417.pdf}

\bibitem{tranckts-sawtooth}
S. W. Amos and M. James, ``Sawtooth generators,'' in
\emph{Principles of Transistor Circuits}, 9th ed. Oxford: Newnes, 2003, ch. 14, pp. 281--292.

\bibitem{ad9958}
Analog Devices, Inc., ``2-Channel, 500 MSPS DDS with 10-Bit DACs,'' AD9958 datasheet,
April 2013 [Revision B].
\url{http://www.analog.com/media/cn/technical-documentation/data-sheets/AD9958.pdf}

\bibitem{az1117c}
Diodes Incorporated, ``Low Dropout Linear Regulator,'' AZ1117C datasheet,
October 2014 [Revision 3--2].
\url{http://www.diodes.com/datasheets/AZ1117C.pdf}

\bibitem{aoe-vreg}
P. Horowitz and W. Hill, ``Voltage regulators and power circuits,'' in
\emph{The Art of Electronics}, 2nd ed. Cambridge: Cambridge, 1989, ch. 6, pp. 307--389.

\bibitem{maswss0162}
M/A-COM Technology, ``GaAs SPST Switch,'' MASWSS0162 datasheet [Revision V3].
\url{http://cdn.macom.com/DataSheets/MASWSS0162.pdf}

\bibitem{mcp1700}
Microchip Technology, ``Low Quiescent Current LDO,'' MCP1700 datasheet,
October 2013 [Revision C].
\url{http://ww1.microchip.com/downloads/en/DeviceDoc/20001826C.pdf}

\bibitem{mc79m00}
ON Semiconductor, ``500 mA Negative Voltage Regulators,'' MC79M00 series datasheet,
July 2013 [Revision 15].
\url{http://www.onsemi.com/pub_link/Collateral/MC79M00-D.PDF}.

\bibitem{l78m05}
STMicroelectronics, ``Precision 500 mA regulators,'' L78M datasheet, June 2014 [Revision 20].
\url{http://www.st.com/web/en/resource/technical/document/datasheet/CD00000447.pdf}

\bibitem{tl431}
Texas Instruments, ``TL43xx Precision Programmable Reference,''
TL431 datasheet, Aug. 2004 [Revised Jan. 2015]. \url{http://www.ti.com/lit/ds/symlink/tl431.pdf}

\bibitem{buckinv}
J. Tucker, ``Using a buck converter in an inverting buck-boost topology,''
\emph{Analog Applications Journal}, Texas Instruments, fourth quarter 2007, pp. 16--19.
\url{http://www.ti.com/lit/an/slyt286/slyt286.pdf}
\end{thebibliography}
