\begin{abstract}
In the current market, electronics lab equipment that can analyze a frequency
response by gain and phase (a vector analyzer) is very expensive, often
reaching into the tens of thousands of dollars.  They are large, heavy
instruments, and are not portable between home, class and a lab. A direct
result of this high cost is that they are generally unobtainable for teachers
to use in classrooms and labs to enhance their education techniques and for
students to use as a hands-on tool for circuit analysis projects.  Due to their
lack of portability, those teachers who do have access to a vector analyzer can
not use its vast functionality for demonstrations of a circuit's behavior in
front of a classroom or in a lab with many students.

It is our goal to remedy this situation by creating a low cost, portable device
that can provide an analysis of gain and phase in a graph.  

This gain/phase analyzer can be produced and sold for approximately \$100. The
device is portable and can be carried between home, work, labs, classrooms, etc
and is very easy to set up with a USB connection to a computer and a power
outlet.  

Additionally, our device is an open source project, with all hardware and
software source available online.  Thus, any capable students or engineers will
have ability to learn how it works and modify the design any way they choose.
This can be a great way for students to gain some hands-on experience in
learning some advanced circuit design techniques and microcontroller
programming.  Additionally, one can apply one’s own creativity and ingenuity to
improve the design of this project; making a better device for future teachers
and students. 
\end{abstract}
